CCVPN: Content Centric Virtual Private Networking

### 2016-12-21 paper/main.tex
adding 1x5 and 5x5 results

\documentclass[conference,letterpaper,10pt]{IEEEtran}
\usepackage{blindtext, graphicx}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

\usepackage[caption=false,font=footnotesize]{subfig}

\usepackage{fixltx2e}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{throughput_pk_1x1}
\caption{Throughput in public key mode}
\label{throughput1x1}
\end{figure}

@@

>>>>

\documentclass[conference,letterpaper,10pt]{IEEEtran}
\usepackage{blindtext, graphicx}

% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

\usepackage[tight,footnotesize]{subfigure}
\usepackage{fixltx2e}

@@

\begin{figure*}[!t]
\centering
  \subfigure[]{\includegraphics[width=2.2in]{throughput_pk_1x1.png}\label{fig_first_case}}
  \hfil
  \subfigure[]{\includegraphics[width=2.2in]{throughput_pk_1x5.png}\label{fig_second_case}}
  \hfil
  \subfigure[]{\includegraphics[width=2.2in]{throughput_pk_5x5.png}\label{fig_third_case}}
\caption{Throughput in public key modee}\label{fig_reenc}
\end{figure*}

@@

el{fig_first_case}}
  \hfil
  \subfigure[]{\includegraphics[width=2.2in]{throughput_pk_1x5.png}\label{fig_second_case}}
  \hfil
  \subfigure[]{\includegraphics[width=2.2in]{throughput_pk_5x5.png}\label{fig_third_case}}
\caption{Throughput in public key modee}\label{fig_reenc}
\end{figure*}
